R for Clinical Study Reports and Submission

### 2022-08-14 tlf-assemble.Rmd
Include rtf-combine.pdf instead of tlf-combine.pdf

```{r}
tlf_path <- c(
  "tlf/tbl_disp.rtf",  # Disposition Table 
  "tlf/tlf_eff.rtf",   # Efficacy Table
  "tlf/tlf_km.rtf"     # KM Plot 
)
```

```{r, out.width = "100%", out.height = "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/tlf-combine.pdf")
```

@@

<details>
<summary>`rtf_assemble1()` source code</summary>
```{r}
#' Assemble RTF files into one single RTF file 
#' 
#' @param path a vector of RTF file path
#' 
#' @export
rtf_assemble1 <- function(path){

  rtf <- lapply(path, readLines)

@@

  for(i in 1:n){
    rtf[[i]] <- rtf[[i]][start[i]:end[i]]
    if(i < n) rtf[[i]] <- c(rtf[[i]], r2rtf:::as_rtf_new_page())
  }
  rtf <- do.call(c, rtf)

  rtf

}
```
</details>

@@

<details>
<summary>`rtf_assemble2()` source code</summary>
```{r}
#' Assemble RTF TLFs
#'
#' Add a set of RTF/TEXT fields into an rdocx object.
#'
#' @param input Character vector of file path.
#' @param output Character string to the output file path.
#' @param landscape Logical vector to determine whether to
#' display files as portrait or landscape.
#'
#' @export
rtf_assemble2 <- function(input, output, landscape = FALSE) {

  input <- normalizePath(input)

@@

```{r}
rtf_assemble2(tlf_path, 
              output = "tlf/rtf-combine-toggle.docx", 
              landscape = c(FALSE, FALSE, TRUE))
```

>>>>

```{r}
tlf_path <- c(
  "tlf/tbl_disp.rtf", # Disposition table
  "tlf/tlf_eff.rtf",  # Efficacy table
  "tlf/tlf_km.rtf"    # K-M plot
)
```

```{r, out.width = "100%", out.height = "400px", echo = FALSE, fig.align = "center"}
knitr::include_graphics("tlf/rtf-combine.pdf")
```

@@

<details>
<summary>`rtf_assemble1()` source code</summary>
```{r}
#' Assemble RTF files into one single RTF file
#'
#' @param path a vector of RTF file path
#'
#' @export
rtf_assemble1 <- function(path) {
  rtf <- lapply(path, readLines)

@@

  for (i in 1:n) {
    rtf[[i]] <- rtf[[i]][start[i]:end[i]]
    if (i < n) rtf[[i]] <- c(rtf[[i]], r2rtf:::as_rtf_new_page())
  }
  rtf <- do.call(c, rtf)

  rtf
}
```
</details>

@@

<details>
<summary>`rtf_assemble2()` source code</summary>
```{r}
#' Assemble RTF TLFs
#'
#' Add a set of RTF/TEXT fields into an rdocx object.
#'
#' @param input Character vector of file path.
#' @param output Character string to the output file path.
#' @param landscape Logical vector to determine whether to
#' display files as portrait or landscape.
#'
#' @export
rtf_assemble2 <- function(input, output, landscape = FALSE) {
  input <- normalizePath(input)

@@

```{r}
rtf_assemble2(
  tlf_path,
  output = "tlf/rtf-combine-toggle.docx",
  landscape = c(FALSE, FALSE, TRUE)
)
```
